---
title: "SAYCAM preprocessing analyses from bounding box outputs"
author: "Bria Long"
date: "6/2020"
output:
  pdf_document: default
  html_document: default
---

# Basic data loading and setup
## Packages
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(stringr)
library(here)
theme_set(theme_few())
```

## Paths to raw outputs & datafiles
```{r}
op_file_dir = here::here("data/op_outputs_per_vid/")
op_files = dir(op_file_dir)
# op_files = op_files [1] # for testing

allocentric_file = here::here("data/raw_data/SAYCAM_allocentric_videos.csv")
to_exclude =read.csv(allocentric_file)

# get INCORRECT videos where allocentric videopoint 
to_exclude <- to_exclude %>%
  filter(allocentric==1) %>%
  rename(vid_name = video)
```

## Main detections: read in bounding box outputs from each vid, summarize and compile.
```{r}
reload_data=TRUE
# instead of loading each vid, load summary...
load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  vid_index = vid_index + 1
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   
   summary_vid_data <- this_vid_data %>%
     group_by(frame, child_id, vid_name, right_side_up, age_days) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)  %>%
     group_by(child_id, vid_name, right_side_up, age_days) %>%
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected), num_detect = length(hand_detected))
   
   
   if (vid_index == 1 ){
     all_vid_data <- summary_vid_data
   }
   else if (vid_index > 1) {
   all_vid_data <- all_vid_data %>%
     full_join(summary_vid_data)
   }
}
}
```

## Cropped detections: crop out detections from outer edges of frames; do so at video level.
```{r}
# cropping paramts
limit_lower =.2
limit_upper =.8
# vid params
y_max = 480
x_max = 640


load(here::here('data/preprocessed_data/all_vid_data_from_bbs_may2020.RData'))

reload_data=TRUE

if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  
   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }
   
   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)

    # don't bother for these files
   if (!this_vid_data$vid_name[1] %in% to_exclude$vid_name){
   
    # for renormalizing y's vids which were run differently this time
   if (this_vid_data$child_id[1]=='Y'){
     this_vid_data <- this_vid_data %>%
      mutate(top = top/y_max, height = height/y_max, left = left/x_max, width = width/x_max)
   }
   
   # now get vid level data
   summary_vid_data_center <- this_vid_data %>%
     mutate(num_frames = length(unique(frame))) %>% # count frames
     mutate(center_y = top + height/2, center_x = left + width/2) %>% # get center_x and y
     filter(center_y<(limit_upper) & center_x<(limit_upper) & center_y>(limit_lower) & center_x>(limit_lower)) %>%   # filter within parameters
     group_by(frame, child_id, vid_name, num_frames, age_days) %>% # group at frame level first
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) %>%
     group_by(child_id, vid_name, age_days, num_frames) %>% # now at the video level
     summarize(num_hands = sum(hand_detected), num_faces = sum(face_detected)) # count how many faces/hands 
   
   # compile vid-level summaries 
   if (vid_index == 1){
     all_vid_data_center <- summary_vid_data_center
   }
   else if (vid_index > 1) {
   all_vid_data_center <- all_vid_data_center %>%
     full_join(summary_vid_data_center)
   }
}
}
}

```


## Gold sample detections only
### Load gold sample annotations
```{R}
## load gold sample annotations
load(here('data/data_cogsci/gold_sample_annotations2020-01-31.RData')) # gold_sample
 
gold_sample_frames <- gold_sample %>%
  select(vid_name, frame) %>%
  mutate(vid_name = str_split(vid_name,"[.]")[[1]][1])

gold_sample_vids <- unique(gold_sample_frames$vid_name)
```

### Get detections from gold sample videos only
```{r}
reload_data=TRUE
# redo gold sample 
if (reload_data){
vid_index = 0
for (vid_file in op_files) {
  
   # to check progress
   vid_index = vid_index + 1
   if ((vid_index %% 100)==0) { print (vid_file) }
   
   # get vid level data
   vid_file_path = paste0(here::here(), '/data/op_outputs_per_vid/', vid_file)
   this_vid_data <- readRDS(vid_file_path)
   this_vid_name_temp <- this_vid_data$vid_name[1]
   
   this_vid_name <- str_split(this_vid_name_temp,"[.]")[[1]][1]
   
   # if it's one of the vids from gold sample
   if (this_vid_name %in% gold_sample_vids){
   # and not excluded
   if (!this_vid_name %in% to_exclude$vid_name){
   
   frames_to_get <- gold_sample_frames %>%
     filter(vid_name == this_vid_name)
  
   # now get vid level data
   gold_sample_op <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0) 
   
   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)
   }
}
}
}
}
```

## Data cleaning
### Choose bins across which to aggregate data
```{r}
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE)
max_age = max(all_vid_data$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

vid_info <- all_vid_data %>%
  select(vid_name, age_days, child_id)
```


### Regualrize vid names & get rid of vids to exclude from allocentric file
```{r}
all_vid_data <- all_vid_data %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])
```

```{r}
all_vid_data <- all_vid_data %>%
  mutate(vid_name_old = vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name) %>%
  mutate(vid_name = vid_name_cleaned) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 

all_vid_data <- all_vid_data %>%
  mutate(vid_name = vid_name_cleaned)

save(all_vid_data, file = here::here('data/preprocessed_data/all_vid_data_from_bbs_june2020.RData'))
```

```{r}
## repeat for center cropped data
all_vid_data_center <- all_vid_data_center %>%
  rowwise() %>%
  mutate(vid_name_cleaned = str_split(vid_name,"[.]")[[1]][1])

all_vid_data_center <- all_vid_data_center %>%
  mutate(vid_name_old = vid_name) %>%
  select(-vid_name) %>%
  filter(!vid_name_cleaned %in% to_exclude$vid_name) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))

all_vid_data_center <- all_vid_data_center %>%
  mutate(vid_name = vid_name_cleaned)

save(all_vid_data_center, file = here::here('data/preprocessed_data/all_centered_vid_data_from_bbs_june2020.RData'))

```

```{r}
all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
  left_join(vid_info) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin)))
save(all_gold_sample_frames_op, file = here::here('data/preprocessed_data/gold_sample_from_bbs_june2020.RData'))
```


### A few videos still need metadata...
```{r}
missing_age <-all_vid_data %>%
  filter(is.na(age_days))
```
