---
title: "Quantifying social information in natural infant visual experience"
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
    \author{{\large \bf Bria Long (bria@stanford.edu)} 
    \AND {\large \bf George Kachergis (kachergis@stanford.edu)} 
    \AND {\large \bf Ketan Jay Agarwal (agrawalk@stanford.edu)} 
    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Street Address \\ Stanford, CA 91305 USA}

abstract: >
    Faces are a critical part of infants' visual experience, as they convey social and 
    linguistic information.
    
keywords: >
    Add your choice of indexing terms or keywords; kindly use a semi-colon; between each term.
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Introduction

Previous work has suggested:
- Relative changes in prevalence of faces vs. hands (Fausey 2016), though perhaps this is driven by infants younger than 4 months of age (e.g., Jayaraman, Fausey, & Smith, 2015; Sugden, Mohamed-Ali, & Moulson, 2014) who see both more frequent and more persistent faces (Jayaraman & Smith, 2018)

- Surprising attention to hand movements and their interactions with objects (Yu & Smith, 2013), particularly in older infants

- Differences in the availability of social information depending on motor abilities (Sanchez, Long et al., 2018 CogSci; @Franchak2011 and more)

One limitation of past work is that it has relied on cross-sectional data, and thus cannot speak to whether these trajectories are present in individual children.

Here, we analyze a longitudinal corpus of head-mounted camera data, leveraging over XX hours of videos from XX children, totaling more than XX frames.  
(briefly describe dataset; sampling strategy: location of two households, number of hours of video, variability in location, etc; reference published paper on what this dataset is, large field of view (fisheye lens))

To do so, we first test and validate novel computer vision methods for extracting social information from these egocentric viewpoints on a small subset of randomly selected frames from the dataset.  We then apply these methods at scale to the larger dataset, allowing us to extract key descriptive variables hypothesized to vary across development.

Part 1: How well can we capture social information using computer vision?
- Description of OpenPose (Figure 1) 
- Description of annotation strategy (24K by Ketan, ~4K on turk, reliability)
- Describe main P/R/F statistics for 24K for faces and hands; interpret. Relatively higher precision vs. recall.
- P/R/F variation across child/age for faces
- Describe possible sources of variation that decrease scores for:
    - Faces: weird viewpoints, occluded/side viewpoint, faces in books
    - Hands: children’s own hands, hands in books, side viewpoints
- Describe additional child vs. hand annotation; P/R/F variation across child vs. adult hands (better for adult hands, still OK for child hands)

Part 2: Access to social information across age
Prevalence of hands vs faces across age (in goldset, full dataset) (Figure 2)
Why so many hands? 
More child hands as in gold set
Cropped analysis

Variation across location contexts (goldset, full dataset)

# Method

If the authors' names are
included in the sentence, place only the year in parentheses, as in
[-@Franchak2011], but otherwise place the entire reference in
parentheses with the authors and year separated by a comma
[@Fausey2016]. List multiple references alphabetically and
separate them by semicolons [@Frank2012; @Smith2011]. 
Use the et. al. construction only after listing all the authors to a
publication in an earlier reference and for citations with four or
more authors.

You might want to display a wide figure across both columns. To do this, you change the `fig.env` chunk option to `figure*`. To align the image in the center of the page, set `fig.align` option to `center`. To format the width of your caption text, you set the `num.cols.cap` option to `2`.


## One-column images

Single column is the default option, but if you want set it explicitly, set `fig.env` to `figure`. Notice that the `num.cols` option for the caption width is set to `1`.

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```


## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
                aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


## Tables


You can use the xtable function in the xtable package.

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                       caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Discussion 

Fausey 2016: 103,383 images; 
Here: 30,000,000 frames; 300 fold increase in data

# Acknowledgements

We would like to thank X and Y for helpful comments, and...

# References 

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}
\noindent
