---
title: Appendix to 'Detecting social information in a dense database of infants’ natural
  visual experience'
date: "`r Sys.Date()`"
output:
  pdf_document: default
---


```{r}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
```


```{r}
## Read in preprocessed data 
load(here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections

## all bounding boxes
load(file=here::here('data/preprocessed_data_2021/bounding_box_summaries.RData'))

```

```{r}
## Load in gold sample detections
load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_all_detections.RData')) 

# all_gold_sample_frames_op_hc = load(here::here('data/preprocessed_data_2021/gold_sample_from_bbs_2021_high_conf_detections.RData')) 
```


```{r}
## summary for all detections
face_hand_by_age <- all_vid_data %>%
  ungroup() %>%
  tidyr::replace_na(list(faces_and_hands=0)) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = sum(num_frames), 
            # prop faces overall
            num_faces = sum(num_faces), 
            num_hands = sum(num_hands), 
            prop_faces = num_faces / num_frames_total, 
            prop_hands = num_hands / num_frames_total,
            # in center FOV
            num_faces_center = sum(num_faces_center, na.rm=TRUE), 
            num_hands_center = sum(num_hands_center, na.rm=TRUE), 
            prop_faces_center = num_faces_center / num_frames_total, 
            prop_hands_center = num_hands_center / num_frames_total,
            # detailed face info
            prop_full_faces = sum(num_full_faces, na.rm=TRUE)/num_frames_total,
            prop_faces_and_hands = sum(faces_and_hands)/num_frames_total,
            # face/hand contingency
            prop_faces_with_hands = sum(faces_and_hands, na.rm=TRUE)/num_faces, 
            prop_hands_with_faces = sum(faces_and_hands, na.rm=TRUE)/num_hands 
            )


all_detections <- face_hand_by_age %>%
  filter(num_frames_total > 2000) %>% # eliminate small data point that skews scaling
  select(prop_faces, prop_hands, num_frames_total, age_day_bin, child_id) %>%
  pivot_longer(cols = c(prop_faces, prop_hands), names_to = "region", values_to = "prop") %>%
  mutate(approach = "uncropped",
         region = ifelse(region == "prop_faces","Faces","Hands"))  
  

```


```{r}
# Function to evaluate detectors
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

# function to return prfs
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

# 

# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected))

 
 ## output prfs
 face_performance = return_prf_short(gold_sample$face_eval_ketan)
 hand_performance = return_prf_short(gold_sample$hand_eval_ketan)

```

```{r}
## Move to appendix
## get out summary by age for goldset hand-labeled frames
vid_info <- all_vid_data  %>%
  select(child_id, vid_name, age_days, age_day_bin)

summary_by_age_gold <- gold_sample %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces= num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
```


```{r}
### Examine gold sample performance by child hands
load(here::here('data/preprocessed_data_2021/child_adult_hand_annotations_by_frame.RData'))

gold_sample_no_child_hands <- gold_sample %>%
  left_join(child_adult_hand_annotations, by=(c("vid_name","frame"))) %>%
  replace_na(list(child_hand_seg = FALSE)) %>% # replace NAs with false (frames not in annotations (NAs) did not have hands) 
  filter(child_hand_seg==FALSE) %>% # now these are counted as frames where OP didn't need to detect something
  mutate(hand_eval_adults = evaluate_detector(hand_present_ketan, hand_detected))

summary_by_age_adult_hands_gold <- gold_sample_no_child_hands %>%
  left_join(vid_info) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_frames_total = n(), num_faces = sum(face_present_ketan), num_hands = sum(hand_present_ketan), prop_faces = num_faces / num_frames_total, prop_hands = num_hands / num_frames_total)
```

```{r}
goldset <- summary_by_age_gold %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "goldset",
         region = ifelse(region == "prop_faces","Faces","Hands"))


goldset_adult_hands <- summary_by_age_adult_hands_gold %>%
  gather(region, prop, prop_faces, prop_hands) %>%
  mutate(approach = "goldset",
         region = ifelse(region == "prop_faces","Faces","Hands"))

```

# Face/hand detections relative to human annotations
```{r goldSetSanity, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion of faces and hands seen as a function of age for each child in the dataset. Data are binned by each week that the videos were filmed and scaled by the number of frames in that age range. Dashed lines show estimated trend lines from proportion of faces/hands in view when analyzing the gold set of frames made by human annotators. Dotted lines show trend lines from the goldset when frames containing children's own hands were excluded." }

ggplot(all_detections %>% filter(child_id %in% c('S','A')), 
       aes(x=age_day_bin, y=prop, 
           size=log10(num_frames_total),
           col=region)) +
  geom_point(alpha=.2) +
  geom_smooth(span=10, aes(weight = num_frames_total), show.legend = FALSE) + 
  geom_smooth(data = goldset_adult_hands, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 2, span=10, se = FALSE) +
  geom_smooth(data = goldset, span=10, aes(weight = num_frames_total), show.legend = FALSE,
              lty = 3, span=10, se = FALSE) +
  ylab('Proportion Detections') + 
  xlab('Age (Months)') +
  ylim(0,.6) +
  facet_grid(.~child_id) + 
  theme_few(base_size=10) +
  ggthemes::scale_color_solarized(name = "") + 
  scale_size_continuous(name = "Detections (Log 10)") +
  theme(legend.text=element_text(size=10)) +
  theme(legend.position="bottom") 

```

# Density of child vs. adults hands in the visual field

```{r} 
### Load turk hand annotations with all bounding boxes (multiple dets per frame)
load(here::here('data/preprocessed_data_2021/hand_annotations_2020-01-29.RData'))

child_hands <- hand_annotations %>%
  filter(label=="Child hand") 

adult_hands <- hand_annotations %>%
  filter(label=="Adult hand")
```

```{r}
### plot centers of the bounding boxes made for child and adult hands
child_hand_plot <- ggplot(child_hands, aes(x=center_x, y=center_y)) +
  geom_point(alpha=.1) + 
  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
  coord_fixed(ratio=1) +
  ggtitle('A. Child hand density') +
  ylim(0,480) +
  xlim(0,640) +
  ylab('') +
  xlab('') +
  theme_few(base_size=10) +
  theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse()
##
adult_hand_plot <- ggplot(adult_hands, aes(x=center_x, y=center_y)) +
  geom_point(alpha=.1) + 
  stat_density_2d(aes(fill = ..level..), geom="polygon", alpha=.8) +
  coord_fixed(ratio=1) +
  ylim(0,480) +
  xlim(0,640) +
  scale_y_reverse() +
  ylab('') +
  xlab('') +
  theme_few(base_size=10) +
    theme(legend.position="none", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  ggtitle('B. Adult hand density')
```

```{r handLocation, fig.env="figure", fig.pos = "h", fig.align = "center", fig.width=6.5, fig.height=3.5, fig.cap = "Density estimates for the child (left) and adult (right) hands that were detected in the 24K frame random gold set; each dot represents the center of a bounding box made by an adult participant. Brighter values indicate more detections."}
cowplot::plot_grid(child_hand_plot, adult_hand_plot, nrow=1)
```

# Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012). 
As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure C1). 
However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.

```{r}
bin_size=7
min_age = min(all_vid_bbs$age_days, na.rm=TRUE)
max_age = max(all_vid_bbs$age_days, na.rm=TRUE)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age) 

all_vid_bbs <- all_vid_bbs %>%
  mutate(age_months = age_days/30.4) %>%
  mutate(age_day_bin = cut(age_days, bins, labels=floor(bin_starts/30.4))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  mutate(avg_center_y = avg_top + avg_height/2, avg_center_x = avg_left + avg_width/2) %>%
  filter(num_detect > 100)

```


```{r, eval=F, include=F}
# add back to text when high-conf BBs are processed:
# We also evaluated OpenPose's performance while restricting detections to high-confidence detections (>.5 confidence, default threshold for visualization). 
#For faces, we found that the F-score was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`. 
#For hands, the F-score for high-confidence detections was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. 
#Thus, as in prior work [@long2020automated], while precision was much higher for both faces and hands, the lower recall for high-confidence detections indicates that these lower-confidence detections still index the presence of social information in the infant view.  
```



```{r faceHandDensity, fig.width=6.5, fig.height=9, fig.cap="Each panel shows the average position of faces and hands in the visual field in a videos from a given age range, i.e., videos when children in the dataset were were 6-31 month-old. Each dot represents the average position from one video within a given age range."}

ggplot(all_vid_bbs %>% filter(label %in% c('face','hand')), aes(x=avg_center_x , y = avg_center_y, size=num_detect, color=label)) +
  geom_point(alpha=.3) + 
  stat_density2d(aes(fill = label, color=label), geom="polygon", alpha=.6) +
  coord_fixed(ratio=.76) +
  # ggtitle('Face/hand density') +
  ylab('') +
  xlab('') +
  theme_few(base_size=14) +
  theme(legend.position="top", axis.text.x=element_blank(), axis.ticks.x=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) +
  scale_y_reverse() +
  facet_wrap(~age_day_bin) +
  guides(size = FALSE) +
  ggthemes::scale_color_solarized(name = "")  +
  ggthemes::scale_fill_solarized(name = "") 
```

# Detection threshold estimations

```{r}
load(here::here("data","preprocessed_data_2021","gold_sample_from_bbs_2021_all_detections_all_thresholds.RData"))

load(here::here('data/preprocessed_data_2021/gold_sample_annotations2020-01-31.RData')) # human annotations
```

```{r}
evaluate_detector <- function(truth, detection) {
  if (truth == TRUE) {
    if (truth == detection) return ("TP") # was face/wrist, detected face/wrist
    else return("FN") # was face/wrist, missed face/wrist
  }
  else {
    if (truth == detection) return("TN") # was not face/wrist, did not detect face/wrist
    else return("FP") # was not face/wrist, detected face/wrist
  }
}

 return_tpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  tpr = tp / (tp + fn)
  return(tpr)
 }

return_fpr = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  tn=sum(eval == "TN")
  fpr = fp / (fp + tn)
  return(fpr)
 }
 
  
```

```{r}
roc_data <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
   mutate(hand_detected = hand_detected>0, face_detected = face_detected > 0) %>% # number = number of faces/hands detected
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) %>%
  group_by(detection_threshold) %>%
  summarize(tpr_faces = return_tpr(face_eval_ketan), fpr_faces = return_fpr(face_eval_ketan), tpr_hands = return_tpr(hand_eval_ketan), fpr_hands = return_fpr(hand_eval_ketan))
```

```{r}
ggplot(data=roc_data, aes(x=fpr_faces, y=tpr_faces, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate')

ggplot(data=roc_data, aes(x=fpr_hands, y=tpr_hands, color=detection_threshold)) +
  geom_point() +
  geom_line() +
  ylim(0,1) +
  xlim(0,1) +
  geom_abline(color = 'grey') +
  xlab('False Positive Rate') +
  ylab('True Positive Rate')

```
# OpenPose Error Analyses
```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
```

```{r}
# add age day bins to gold_sample
load(file=here::here('data/preprocessed_data_2021/all_vid_data_from_bbs_all_detections.RData')) # all detections
bin_size = 7 # days
min_age = min(all_vid_data$age_days, na.rm=TRUE) # 182
max_age = max(all_vid_data$age_days, na.rm=TRUE) # 966
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

gold_sample <- gold_sample %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) 
```

```{r}
 return_prf = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  num_detect = length(eval)
  out <- data.frame(p,r,f,num_detect)
  return(out)
 }

```

```{r}
prf_by_age_faces <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_age_hands <-  gold_sample %>%
  group_by(child_id, age_day_bin) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```


```{r}

prf_by_age_faces$age_day_bin = as.numeric(prf_by_age_faces$age_day_bin)

prf_by_age_hands$age_day_bin = as.numeric(prf_by_age_hands$age_day_bin)

ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Face detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')


ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Hand detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')


# p2 = ggplot(prf_by_age_faces, aes(x=age_day_bin, y=p, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Precision - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# 
# p3 =ggplot(prf_by_age_faces, aes(x=age_day_bin, y=r, col=child_id, size=num_detect)) +
#   geom_point(alpha=.5) +
#   geom_smooth(span=10, alpha=.1)  +
#   ylim(0,1) +
#   ylab('Recall - Face detection')+
#   xlab('Age (months)') +
#   theme(legend.position= 'none')
# #
# ggarrange(p1,p2,p3)

```

```{r}

```

```{r}
load(here::here('data/preprocessed_data_2021/saycam_metadata.RData')) # meta

num_videos_annotated = sum(!is.na(meta$Location))
videos_included = sum(!is.na(meta$Location) & meta$count_locations==1)
```

```{r}
gold_sample_by_location <- gold_sample %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 

```

```{r}
prf_by_location_faces <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$face_eval_ketan)) %>%
  filter(num_detect > 50)

prf_by_location_hands <-  gold_sample_by_location %>%
  group_by(Location) %>%
  do(return_prf(.$hand_eval_ketan)) %>%
  filter(num_detect > 50)
```

```{r}


ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Face detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```

```{r}
ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Hand detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```

