---
title: "saycam full dataset analysis"
author: "Bria Long"
date: "1/9/2020"
output: html_document
---

# Basic data loading and setup
## Packages
```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(assertthat)
library(ggthemes)
library(lme4)
library(langcog)
library(viridis)
library(magick)
library(stringr)
library(egg)
theme_set(theme_few())
```

## Read in data 
### Load preprocessed and filtered detections


```{r}
load('../data/openpose_detections_filtered_threekids.RData') #d_all

##
load('../data/openpose_detections_filtered_cropped_allthreekids.RData') # d_cropped
```



### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_all$age_days)
max_age = max(d_all$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d_all <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_all$age_day_bin = as.numeric(as.character(d_all$age_day_bin))

d_all$face_openpose = as.logical(d_all$face_openpose)
d_all$hand_openpose = as.logical(d_all$hand_openpose)
d_all$person_openpose = (as.logical(d_all$face_openpose) | as.logical(d_all$hand_openpose))
d_all$both_openpose = (as.logical(d_all$face_openpose) & as.logical(d_all$hand_openpose))
```


# Full dataset; all detection
## How do face/hand detection vary by age? 
### Compute summary statistics
```{r}
summary_by_age <- d_all %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1))) %>%
  mutate(age_day_bin = as.numeric(as.character(age_day_bin))) %>%
  group_by(age_day_bin, child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_openpose) / num_detect, face_or_hand = sum(person_openpose)/ num_detect, face_and_hand = sum(both_openpose)/ num_detect) 

# under 24 months
summary_by_age_limited <- summary_by_age %>%
  filter(age_day_bin < 24.1)

```
  
### Plot faces x age x child
```{r}
(faces <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  geom_smooth(span=10) + 
  ylab('Proportion Faces') + 
     theme_few(base_size=16) +
  xlab('Age bin (months)') +
  ylim(0,.5) +
  theme(legend.position="none"))
```

### Plot hands x age x child
```{r}
(hands <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
     theme_few(base_size=16) +
  ylab('Proportion Hands') + 
  xlab('Age bin (months)') +
  ylim(0,.5)+
  theme(legend.position="none"))
```

### Plot Faces - Hands x age x child:  Key plot for fausey comparison
```{r}
## faces - hands
(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  theme_few(base_size=16) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)')+
  theme(legend.position="right"))
```

### Compiled plot
```{r}

ggarrange(faces,hands,face_v_hand, nrow=1)
```


### Plot Face OR hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_or_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Face OR Hand') + 
  xlab('Age bin')
```

### Plot Face AND hand x age x child
```{r}
ggplot(summary_by_age, aes(x=age_day_bin, y=face_and_hand, size=num_detect, col=child_id)) +
  geom_point(alpha=.5) +
  geom_smooth(span=10) + 
  ylab('Proportion Face AND Hand') + 
  xlab('Age bin')
```
## By location
### Summarize faces vs hands by location

```{r}

check <- d_all %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(num_frames = n())

face_hand_by_location <- d_all %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_openpose), num_detect = length(face_openpose))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_by_location_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="prop_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean)) 

faces_by_location_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="prop_faces") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean)) 

faces_vs_hands_to_plot <- face_hand_by_location %>%
  multi_boot_standard(col="faces_vs_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location) %>%
  mutate(Location = fct_reorder(Location, mean)) 

```

### Plot faces and hands by location
```{r}
(plot_faces_loc = ggplot(faces_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Faces')+
   theme(legend.position = "none")) 
  
(plot_hand_loc = ggplot(hands_by_location_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Hands') +
  theme(legend.position = "none"))

(plot_hands_vs_faces = ggplot(faces_vs_hands_to_plot, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  ylab('Proportion Faces - Hands')) 


ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces, nrow=1)
```


### what percentage of the dataset is this? 
```{r}
percentage_of_dataset = sum(faces_vs_hands_to_plot$num_detect)/length(d_all$frame)
```


# Cropped analysis

### Make bins across which to analyze data
```{r}
bin_size = 7
min_age = min(d_cropped$age_days)
max_age = max(d_cropped$age_days)
bin_starts = seq(min_age-1, max_age+1,bin_size)
bins = c(bin_starts, max_age)

d_cropped <- d_cropped %>%
  mutate(age_day_bin = cut(age_days, bins, labels=round(bin_starts/30,1)))
d_cropped$age_day_bin = as.numeric(as.character(d_cropped$age_day_bin))

d_cropped$face_openpose = as.logical(d_cropped$face_openpose)
# d_cropped$hand_openpose = as.logical(d_cropped$hand_openpose)

```

## Faces vs hands
### Summary statistics
```{r}
summary_by_age_cropped <- d_cropped %>%
  group_by(age_day_bin,child_id) %>%
  summarize(num_detect = length(face_openpose), prop_faces = sum(face_openpose) / num_detect,  prop_hands = sum(hand_detected_cropped) / num_detect) 
# 
# summary_by_age_cropped_limited <- summary_by_age_cropped %>%
#   filter(age_day_bin < 24.1)
```


### Plot hands x age x child
```{r}
(hands_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10) + 
  ylab('Proportion Hands (Cropped)') + 
  xlab('Age bin (months)') +
  ylim(0,.5))
```

### Plot faces vs. hands for cropped frames
```{r}
(face_v_hand_cropped <- ggplot(summary_by_age_cropped, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.4) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  ggtitle('(B). Upper 60% of FOV'))


(face_v_hand <- ggplot(summary_by_age, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.4) +
  geom_smooth(span=10) + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands') + 
  xlab('Age (months)') +
  ylim(-.3, .3) +
  theme(legend.position = "none") +
  ggtitle('(A). Entire FOV'))

ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

```

```{r}
ggplot(summary_by_age_cropped_limited, aes(x=age_day_bin, y=prop_faces - prop_hands, size=num_detect, col=child_id)) +
  geom_point(alpha=.8) +
  geom_smooth(span=10, method='lm') + 
  theme_few(base_size=18) +
  ylab('Proportion Faces - Hands (CROPPED)') + 
  xlab('Age (months)')

ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

```


### Side by side plots for cropped comparison
```{r}
ggarrange(hands, hands_cropped, nrow=1)
ggarrange(face_v_hand, face_v_hand_cropped, nrow=1)

```

## By location
### Summarize

### Load SAYCAM metadata from csv file
```{r}
metadata_file = "../data/SAYcam-2019-12-0922_54_28.csv"

meta=read.csv(metadata_file) %>%
  rowwise() %>%
  mutate(vid_name = str_split(File.Name,"[.]")[[1]][1]) %>%
  mutate(count_locations = length(str_split(Location,',')[[1]]))

# collapse duplicate labels
meta$Location[meta$Location=='Bedroom Alice/Sam'] = 'Bedroom'

```

### Join with cropped datasets and summarize
```{r}
face_hand_by_location_cropped <- d_cropped %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) %>%
  group_by(Location,child_id,age_day_bin) %>%
  summarize(prop_faces = mean(face_openpose), prop_hands = mean(hand_detected_cropped), num_detect = length(hand_detected_cropped))  %>%
  filter(num_detect > 9000) %>% ## 9000 frames = 5 minutes of video at 30 fps %>%
  mutate(faces_vs_hands = prop_faces - prop_hands)

hands_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean)) 

faces_by_location_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="prop_faces") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean)) 

faces_vs_hands_to_plot_cropped <- face_hand_by_location_cropped %>%
  multi_boot_standard(col="faces_vs_hands") %>%
  ungroup %>%
  left_join(face_hand_by_location_cropped) %>%
  filter(!is.na(ci_lower)) %>% # if we didn't have enough points to make a CI, filter
  mutate(Location = fct_reorder(Location, mean)) 


```

### Plot cropped detections by location
```{r}
(plot_faces_loc_cropped = ggplot(faces_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_faces, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Faces')+
   theme(legend.position = "none")) 
  
(plot_hand_loc_cropped = ggplot(hands_by_location_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=prop_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(0,.6) +
  coord_flip() + 
  ylab('Proportion Hands') +
  theme(legend.position = "none"))

(plot_hands_vs_faces_cropped = ggplot(faces_vs_hands_to_plot_cropped, aes(x = Location, y = mean, col=child_id)) + 
  geom_point(aes(x=Location, y=faces_vs_hands, size=num_detect), alpha=.2, position = position_dodge(width=.3)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width=.3)) +
  # ylim(-.4,.4) +
  coord_flip() + 
  ylab('Proportion Faces - Hands')) 
  

# ggarrange(plot_faces_loc, plot_hand_loc,plot_hands_vs_faces)
ggarrange(plot_faces_loc_cropped, plot_hand_loc_cropped,plot_hands_vs_faces_cropped, nrow=1)
# ggarrange(plot_hands_vs_faces,plot_hands_vs_faces_cropped, nrow=1)

```




# Inferential statistics
### Entire age range
```{r}
summary_by_age_cropped$num_detect <- scale(summary_by_age_cropped$num_detect)

model_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + (1 | child_id), data = summary_by_age_cropped_limited)
summary(model_cropped)
```

### Full dataset
```{r}
summary_by_age_cropped_limited$num_detect <- scale(summary_by_age_cropped_limited$num_detect)

model_limited_cropped <- glmer(prop_faces - prop_hands ~ age_day_bin + num_detect + (1 | child_id), data = summary_by_age_cropped_limited)
summary(model_limited_cropped)


```


# Analyze most frequent activities by location
```{r}
frames_by_video <- d_all %>%
  group_by(vid_name) %>%
  summarize(num_frames = n())

activity_by_location <- meta %>%
  filter(!is.na(Location)) %>%
  filter(!Activity=='N/A') %>%
  filter(!is.na(Activity)) %>%
  filter(!Location=='N/A') %>%
  filter(count_locations==1) %>%
  select(vid_name, Location, Activity) %>%
  mutate(Activity = strsplit(as.character(Activity), ",")) %>% 
  unnest(Activity)

# fix typo in annotations
activity_by_location$Activity[activity_by_location$Activity=='Talking Walk']='Taking Walk'
```

### Plot activities by context
```{r}
activity_contexts <-  activity_by_location %>%
  left_join(frames_by_video) %>%
  filter(!Activity=='N/A') %>%
  group_by(Location,Activity) %>%
  summarize(count_frames = sum(num_frames)) %>%
  filter(count_frames > 9000) 

ggplot(activity_contexts, aes(Location, y=Activity)) +
  geom_tile(aes(fill = count_frames)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  coord_flip()

```
