---
title: "Bounding Box Analysis"
author: "George"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)

require(tidyverse)
require(data.table)
require(here)
require(stringr)
```

## Load Data

Detections by type:

```{r load-data}
load(here("data/all_bounding_boxes.RData"))
#summary(df)
table(df$label)
```

## Filter Weird Data

We'll also get rid of detections in videos that were not named with the standard format (and therefore we could not extract age from; e.g. 161384-Baby_Scene videos).
We may also want to get rid of detections below some level of mean confidence (a skewed distro: most <.1): we'll start with $\geq 0.1$.

```{r filter-data, echo=FALSE}
# normalize Y vids height=480, width=640

sdf <- df %>% filter(!is.na(age_days),
                     area>.0001, # keep detections larger than .01*.01
                     mean_confidence > .3)


sdf <- sdf %>% mutate(age_months = round(age_days / 30.42))
```

Keeping `r round(nrow(sdf)/nrow(df),3)*100`% of the detections.

## Detection size by type

Detected people are generally much larger than faces, or hands (which are quite small) -- all very reasonable.

```{r}
sdf %>% ggplot(aes(x=area, fill=label)) + 
  geom_histogram(alpha=.5) + theme_bw() #+ facet_wrap(~age_months)
```

```{r}
hands_by_age <- sdf %>%
  filter(label=="hand") %>%
  group_by(vid_name, age_months, child_id) %>% # do per frame ?
  summarize(N = n(), avg_area = mean(area))

faces_by_age <- sdf %>%
  filter(label=="face") %>%
  group_by(vid_name, age_months, child_id) %>%
  summarize(N = n(), avg_area = mean(area))

poses_by_age <- sdf %>%
  filter(label=="pose") %>%
  group_by(vid_name, age_months, child_id) %>%
  summarize(N = n(), avg_area = mean(area))
```


```{r}
ggplot(hands_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Hand size by #') +
  facet_wrap(~age_months) + theme_bw()

ggplot(faces_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Hand size by #') +
  facet_wrap(~age_months) + theme_bw()

ggplot(poses_by_age, aes(x=N, y=avg_area, col=child_id)) +
  geom_jitter(alpha=.2) +
  ggtitle('Pose size by #') +
  facet_wrap(~age_months) + theme_bw()
```

